% ============================================================================
% Abstract
% ============================================================================

\chapter*{Abstract}

\vspace{1cm}

Online furniture retail in Egypt suffers from a critical visualization gap: shoppers cannot see how products will look in their own spaces, leading to cart abandonment rates exceeding 90\%. Meanwhile, professional interior design services cost 500--2,000 EGP per room---prohibitive for most households. IntelliRoom bridges this gap with an AI-powered interior design platform built specifically for the Egyptian e-commerce market.

\vspace{0.5cm}

\textbf{IntelliRoom} leverages a production-ready generative AI engine built on \textbf{Flux2Klein 4B}---a state-of-the-art Diffusion Transformer---combined with SAM2 for precision image segmentation, ControlNet for structural preservation, and Florence-2 for intelligent object detection, all orchestrated through ComfyUI workflows. Users upload a room photograph and receive high-fidelity redesign results while the system simultaneously identifies and retrieves visually matching furniture from Egyptian retailers.

\vspace{0.5cm}

The furniture retrieval engine implements a novel two-plane architecture: a local FastAPI orchestrator (ChromaDB vector database, semantic taxonomy snapper) connected via zrok tunneling to a remote GPU inference server running \textbf{RF-DETR} for furniture detection, \textbf{SigLIP2 so400m} for 1152-dimensional visual embeddings, and \textbf{Qwen3-VL 4B}---selected through an empirical ablation study over 2B/4B/8B variants---for taxonomy tagging. This pipeline enables accurate, semantically-constrained product retrieval from the Egyptian furniture catalog at commercial scale.

\vspace{0.5cm}

The platform delivers a complete full-stack solution: a React.js frontend, a Node.js/Express REST API with asymmetric JWT (RS256) authentication, MongoDB with 14+ schemas, a Fawaterk-integrated subscription system, a community gallery, and a plugin marketplace. The result is a commercially viable platform that democratizes interior design visualization for Egyptian homeowners and directly converts design inspiration into purchasable local furniture.

\vspace{1cm}

\textbf{Keywords:} Artificial Intelligence, Interior Design, Flux2Klein, Computer Vision, Image Segmentation, Generative AI, Egyptian E-Commerce, Furniture Retrieval, RF-DETR, SigLIP2, Qwen3-VL, ComfyUI, Vector Database, SAM2, ControlNet

