% ============================================================================
% Acknowledgements
% ============================================================================

\chapter*{Acknowledgements}

\vspace{1cm}

First and foremost, we would like to express our sincere gratitude to \textbf{Allah (God)} for granting us the strength, patience, and perseverance to complete this graduation project.

\vspace{0.5cm}

We extend our deepest appreciation to our supervisor, \textbf{Prof. Gamal A. Ebrahim}, for his invaluable guidance, continuous support, and expert advice throughout this project. His insights into artificial intelligence and computer vision have been instrumental in shaping our technical approach and research methodology.

\vspace{0.5cm}

We are grateful to the \textbf{Faculty of Engineering, Ain Shams University}, and specifically the \textbf{Department of Computer and Systems Engineering}, for providing us with the educational foundation and resources necessary to undertake this ambitious project.

\vspace{0.5cm}

Special thanks to the open-source communities behind \textbf{ComfyUI}, \textbf{SAM2}, \textbf{Florence-2}, and other AI tools that made this project technically feasible. Their contributions to democratizing AI technology have enabled students and researchers worldwide to build innovative solutions.

\vspace{0.5cm}

We acknowledge the \textbf{Egyptian interior design community} for their valuable input on cultural preferences, traditional aesthetics, and local market needs. Their feedback helped us understand the real-world requirements that distinguish IntelliRoom from generic Western-focused solutions.

\vspace{0.5cm}

Finally, we express our heartfelt gratitude to our \textbf{families and friends} for their unwavering support, encouragement, and understanding throughout the demanding journey of this graduation project.

\vspace{1cm}

\begin{flushright}
    \textit{The IntelliRoom Team}\\
    Cairo, January 2026
\end{flushright}
